>

### 2024-11-06 docs/index.qmd
Plan the modelling procedures
Include the report directly to the index
This patch will avoid recursive file searching, which apparently introduces error when run with 'targets'.

::: {.content-visible when-meta="in.report"}
{{< include exec-summary/_report.qmd >}}
:::

@@

>>>>

## Analytical procedures

{{< include exec-summary/_source-data.qmd >}}

{{< include exec-summary/_preprocessing.qmd >}}

{{< include exec-summary/_measure-eigen.qmd >}}

{{< include exec-summary/_descriptive.qmd >}}

{{< include exec-summary/_seasonality.qmd >}}

{{< include exec-summary/_arima.qmd >}}

{{< include exec-summary/_spectral.qmd >}}

## Highlighted findings

{{< include exec-summary/_result-highlights.qmd >}}

::: {.content-visible when-profile="summary"}

\uselandscape

## Excerpt on findings

### Pair plot

tar_read(plt_pair)[[17]]

### Dot plots on weekly time-series

tar_read(plt_dot_week)[[1]]

### Differenced time-series on a weekly interval

tar_read(plt_dot_diff_week)[[1]]

### Exploring seasonality within the number of medication claims

tar_read(plt_period_month)[[1]]
tar_read(plt_acf_diff_month)[[1]]
tar_read(plt_pacf_diff_month)[[1]]

### Exploring ARIMA model

tar_read(plt_arima_forecast_n_claim)[[17]]

### Decomposed time-series with SSA

tar_read(plt_ssa_recon_n_claim)[[17]]

\normalpapersize

:::

@@

::: {.content-visible when-profile="models"}
{{< include exec-summary/_models.qmd >}}
:::
